### 2020-12-17 07_cost_bounds.tex
Updates from Overleaf

Following from Lemma \ref{lem:transferdomination}, the current analysis studies the dual arm costs in the randomized unit tabletop setting, with $c_t$ as the cost measure per unit distance. 
For the $2$-arm setting, assume for simplicity that each arm's volume is represented as a disc of some radius 
$r$. For obtaining a $2$-arm solution, we partition the $n$ objects randomly 
into two piles of $\frac{n}{2}$ objects each; then obtain two initial solutions 
similar to the single arm case. It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves 
should add up to approximately $(c_{pd} + 0.52c_t)n$.

\begin{theorem}
	\textit{For rearranging objects with non-overlapping starts and goals that are
	uniformly distributed in a unit square,  a $2$-arm solution can have an 
	asymptotic improvement of $\frac{1}{2}$ over the single arm solution. }
	\label{thm:karm}
\end{theorem}

\textit{Proof: }
From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
solution that is collision-free. Assume that pickups 
and drop-offs can be achieved without collisions between the two arms, which 
can be achieved with properly designed end-effectors. The main overhead 
is then the potential collision between the two (disc) arms during transfer 
and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
with, an arm may travel a path formed by $n + 1$ straight line 
segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
two end-effector trajectories where potential collision may happen. However,
because for the transfers and transits associated with one pair of objects (one 
for each arm) can have at most four intersections, there are at most 
$2n$ potential collisions to handle. For each intersection, let one 
arm wait while letting the other circling around it, which incurs a cost that is bounded by $2\pi \cdot
r \cdot c_t$.

Adding up all the potential extra cost,  
% that a $2$-arm solution has 
a cumulative cost is obtained as 
% \begin{align}\label{eq:dual-cost-distance} 
% C_{dual} = C_{single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n.
% \end{align}

@@

\noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$ 
$c_t$ is a distance (e.g., energy) cost. Upon considering the maximum of the two arc lengths or makespan (Eq.~\ref{eq:cost_function}),
the $2$-arm cost becomes $C_{\rm dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$.
% \vspace{-0.1in}
% \begin{equation}\label{eq:dual-cost-time}
% C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t
% \vspace{-0.1in}
% \end{equation}
% {\centerline
% {
% $C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$
% }
% }
The cost ratio is
%\vspace{-0.1in}
\begin{align*}\label{eq:makespan-ratio}
\frac{C_{\rm dual}^t}{C_{\rm single}} &\approx 
\frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
\\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;.\numberthis
% \vspace{-0.1in}
\end{align*}

@@

%This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.

%\vspace{-0.08in}
\commentadd{
%\begin{theorem}
%For rearranging objects with non-overlapping starts and goals that are
%uniformly distributed in a unit square,  a $2$-arm solution can have an 
%asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
%\label{thm:karm}
%\end{theorem}
}

\tase{
\begin{theorem}
	\textit{For rearranging objects with non-overlapping starts and goals that are
	uniformly distributed in a unit square,  a $k$-arm solution can have an 
	asymptotic improvement of $\frac{1}{k}$ over the single arm solution. }
\end{theorem}

\textit{Proof:}	
%\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
\commentadd{The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
	for each arm to work with. Consider the transfers and transits of a set of $k$ 
	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
	can be achieved in a bounded region with a perimeter of $O(kr)$. 
	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential 
	extra cost,  a $k$-arm solution has a cumulative cost

	The cost ratio is
	\vspace{-0.1in}
	\begin{align*}\label{eq:kmakespan-ratio}
	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
	% \vspace{-0.1in}
	\end{align*}

%	\begin{theorem}
%		For rearranging objects with non-overlapping starts and goals that are
%		uniformly distributed in a unit square,  a $k$-arm solution can have an 
%		asymptotic improvement of $\frac{1}{k}$ over the single arm solution. 
%	\end{theorem}
}
% \rahul{Need to verify this line of reasoning}

\begin{theorem}
	\textit{For rearranging objects with non-overlapping starts and goals that are 
	uniformly distributed in a unit square,  a randomized $2$-arm \textit{synchronized} solution can have an 
	asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. }
\end{theorem}

\textit{Proof:} The synchronization assumption changes the expected cost of the solution. The random partitioning of the $n$ objects into two sets of $\frac{n}{2}$ object with a random ordering of the objects yields $\frac{n}{2}$ pairs of objects transfers, which dominate the total cost for large $n$. The cost~(Eq.~\ref{eq:cost_function}) of $\frac{n}{2}$ synchronized transfers ($\coma_i$) includes $\frac{n}{2}c_{pd}$ and $C^{\rm sync}_{sg} \approx (\mathtt{E}(max(l_1,l_2))c_t)\frac{n}{2}$, where $\mathtt{E}(max(l_1,l_2))$ is the expected measure of the max of lengths $l_1$,$l_2$ of two randomly paired transfers. Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup\cite{Shome2018WAFR}, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$ . 
% (Section \ref{sec:appendix}).

\tase{
\begin{lemma}
	Expected measure of the maximum of lengths of two random lines on an unit square is $ 0.66 $.
\end{lemma}

\textit{Proof:} Prior work \cite{ghosh1951random} defines the \textit{probability distribution function (pdf)} of lengths($l$) of randomly sampled lines in a rectangle.
% of sides $a,b, \ \ a\geq b$.
% as 
%\begin{align*}
%p(l) &= (\frac{4l}{a^2b^2})\phi(l)\\
%\phi(l)&= \frac{1}{2}\pi a b - a l - b l + \frac{1}{2} l^2, \ \ l\in[0,b]\\
%\phi(l)&= ab \sininv(\frac{b}{l}) + a. \sqrt[]{(l^2-b^2)} - al - \frac{1}{2}b^2, \ \ l\in[b,a]\\
%\phi(l)&= ab\{\sininv(\frac{b}{l})-\cosinv(\frac{a}{l})\} + a\sqrt[]{(l^2-b^2)} + b\sqrt[]{(l^2-a^2)} \\
%&- \frac{1}{2}(l^2+a^2+b^2),\ \ l\in[a,\sqrt[]{(a^2+b^2)}]
%\end{align*}

%In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
In the unit square model, substituting the values for the dimensions of the sides of the rectangle with $1$, the \textit{pdf} can be simplified as follows.
\begin{align*}
p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l,\\ &\ l\in[1,\sqrt[]{2}]
\end{align*}

Assuming two random sets of lines, representing transfers in a random split of objects between two arms, we need the expected value of the maximum of these pairwise lengths ie., $\mathtt{E}(max(l_1,l_2)), \ \ l_1,l_2\ i.i.d, \ \ l_1 \sim p, l_2 \sim p$.
This is estimated using the \textit{pdf} obtained. 
\begin{align*}
\mathtt{E}(max(l_1,l_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1\\&\approx 0.663
\end{align*}
The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
\commentadd{
%	\begin{figure}[h]
%		\centering
%		%	\vspace{-0.3in}
%		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
%		\caption{Empirical cost ratio versus the estimate}
%		\label{fig:mcbounds}
%	\end{figure}

	Prior work~\cite{santalo2004integral} offered an estimate for the expected length of a transit path $C_{sg}$ in terms of the expected length of a line segment, $0.52$, in a randomized setting in an unit square. With the current estimate of $0.663$ for the maximum of two such randomly sampled line segments, it follows that, the expected makespan or maximum of distances cost will use this estimate.\qed

@@

This means $C_{\rm dual}^{\rm sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$.
% \vspace{-0.1in}
% \begin{equation}\label{eq:synchronized-cost}
% C_{dual}^{sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t
% \vspace{-0.1in}
% \end{equation}
% {\centerline
% {
% $C_{dual}^{sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$
% }
% }
The synchronized cost ratio is
%\vspace{-0.1in}
\begin{align*}\label{eq:synchronized-ratio}
\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} &\approx 
\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
\\&= \frac{1}{2} + \frac{ (0.07 + 4\pi r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
%\vspace{-0.1in}
\end{align*}

When $\frac{c_t}{c_{pd}}$ is small, even the synchronized $2$-arm solution provides an improvement of $\frac{1}{2}$. For the case when both $r$ and $c_{pd}$ are small, we observe that the ratio approaches $0.636$. 
\commentdel{Fig \ref{fig:bounds} confirms empirically that in randomized trials on an unit square, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, converges to the calculated estimate (red line).}

\tase{
	\begin{figure}[h]
		\centering
		%	\vspace{-0.3in}
		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
		\caption{Empirical cost ratio versus the estimate}
		\label{fig:mcbounds}
	\end{figure}
	As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$. Fig \ref{fig:mcbounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
}

\qed
%\vspace{-0.08in}
%\begin{theorem}
%For rearranging objects with non-overlapping starts and goals that are 
%uniformly distributed in a unit square,  a randomized $2$-arm synchronized solution can have an 
%asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. 
%\end{theorem}

\commentadd{
\noindent \textbf{Note on bounds:} Even though the proposed simplified model does not apply immediately costs and collision volumes in general configuration spaces, experiments indicate that the speedups exist in these spaces as well.
}
% \rahul{this paragraph is phrased contradictorily. It makes sense if the first sentence is for asynchronous cases.}
% We note that the same can be said for a {\em synchronous} $2$-arm solution if
% when $c_t/c_{pd}$ is small. 
% Under the synchronization assumption, $C_{dual}^t$
% is no longer necessarily expected to be $\frac{C_{single}}{2}$ for large $n$. 
% Experiments in the next section indicate that improvements over single arm solutions in practical settings.

>>>>

% This section studies the dual arm costs in the randomized unit tabletop setting, where $c_t$ is the cost measure per unit distance.  For the $2$-arm setting, assume for simplicity that each arm's volume is represented as a disc of some radius $r$. For obtaining a $2$-arm solution, first partition the $n$ objects randomly into two sets of $\frac{n}{2}$ objects each. Then, obtain the two initial solutions similar to the single arm case.  It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves should add up to approximately $(c_{pd} + 0.52c_t)n$. The reasoning follows Lemma \ref{lem:transferdomination}, which states that transfers dominate the cost of the solution.

% \begin{theorem}
% 	\textit{A $2$-arm solution can have an asymptotic improvement of $\frac{1}{2}$ over the single arm solution for rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square}
% 	\label{thm:karm}
% \end{theorem}

% \textit{Proof: }
% From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
% solution that is collision-free. Assume that pickups and drop-offs can be achieved without collisions between the two arms, which can be achieved with properly designed end-effectors. The main overhead is then the potential collision between the two (disc) arms during transfer and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
% with, an arm may travel a path formed by $n + 1$ straight line 
% segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
% two end-effector trajectories where potential collisions may happen. Nevertheless, since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle. For each intersection, let one 
% arm wait while the other circles around the first arm, which incurs a cost that is bounded by $2\pi \cdot r \cdot c_t$.

% Adding up all the potential cost that a $2$-arm solution can incur, the following cumulative cost is obtained:
% % \begin{align}\label{eq:dual-cost-distance} 
% % C_{dual} = C_{single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n.
% % \end{align}

% {\centerline
% {
% $C_{\rm dual} = C_{\rm single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n\;.$
% }
% }

% \noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$, and
% $c_t$ is a distance (e.g., energy) cost. Upon considering the maximum of the two arc lengths or makespan (Eq.~\ref{eq:cost_function}),
% the $2$-arm cost becomes $C_{\rm dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$.
% % \vspace{-0.1in}
% % \begin{equation}\label{eq:dual-cost-time}
% % C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t
% % \vspace{-0.1in}
% % \end{equation}
% % {\centerline
% % {
% % $C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$
% % }
% % }
% The cost ratio is
% %\vspace{-0.1in}
% \begin{align*}%\label{eq:makespan-ratio}
% \frac{C_{\rm dual}^t}{C_{\rm single}} &\approx 
% \frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
% \\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;\numberthis \label{eq:dualasync}
% % \vspace{-0.1in}
% \end{align*}

% \commentdel{
%  \begin{wrapfigure}{r}{1.4in}
% %  \vspace{-.45in}
% 	\centering
%     \includegraphics[width=1.4in]{figures/monte_carlo}
% %    \vspace{-.4in}
% 	\caption{Empirical cost ratio versus the estimate}
%   	\label{fig:bounds}
% %    \vspace{-.4in}
% \end{wrapfigure}
% }

% When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $2$-arm 
% solution is roughly half as costly as the single arm solution. On 
% the other hand, in this model a $2$-arm solution does not do better than $\frac{1}{2}$ of the single arm solution. $ \qed $

% %This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.

% %\vspace{-0.08in}
% \commentadd{
% %\begin{theorem}
% %For rearranging objects with non-overlapping starts and goals that are
% %uniformly distributed in a unit square,  a $2$-arm solution can have an 
% %asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
% %\label{thm:karm}
% %\end{theorem}
% }

% \tase{

% The following argument generalizes Theorem~\ref{thm:karm} to the case of $k$-arms.

% \begin{theorem}
% 	\textit{A $k$-arm solution can have an 
% 	asymptotic improvement of $\frac{1}{k}$ over the single arm solution, when rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square.}
% \end{theorem}

% \textit{Proof:}	
% %\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
% \commentadd{The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
% 	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
% 	for each arm to work with. Consider the transfers and transits of a set of $k$ 
% 	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
% 	can be achieved in a bounded region with a perimeter of $O(kr)$. 
% 	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
% 	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential cost that can be incurred,  a $k$-arm solution has a cumulative cost of:

% 	{\centerline
% 		{
% 			$C_{\rm k{\text-}arm} = C_{\rm single} + nf(k,r)c_t \approx (c_{pd} + 0.52c_t + f(k,r)c_t)n\;.$
% 		}
% 	}

% 	\noindent For fixed $k$ and small $r$, $C_{\rm k{\text-}arm}$ is almost the same as $C_{\rm single}$.
% 	%, $c_t$ is a distance (e.g., energy) cost. 
% 	Upon considering the maximum of the two arc lengths or makespan,
% 	the $k$-arm cost becomes $C_{\rm k{\text-}arm}^t \approx (c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t$.

% 	The cost ratio is
% % 	\vspace{-0.1in}
% 	\begin{align*}\label{eq:kmakespan-ratio}
% 	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
% 	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
% 	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
% 	% \vspace{-0.1in}
% 	\end{align*}

% 	When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $k$-arm 
% 	solution is roughly $\frac{1}{k}$ as costly as the single arm solution. On 
% 	the other hand, in this model a $k$-arm solution does not do better than $\frac{1}{k}$ of 
% 	the single arm. \qed

% %	\begin{theorem}
% %		For rearranging objects with non-overlapping starts and goals that are
% %		uniformly distributed in a unit square,  a $k$-arm solution can have an 
% %		asymptotic improvement of $\frac{1}{k}$ over the single arm solution. 
% %	\end{theorem}
% }
% % \rahul{Need to verify this line of reasoning}

% }

This section studies the dual arm costs in the randomized unit tabletop setting, where $c_t$ is the cost measure per unit distance.  Assume for simplicity that each arm's volume is represented as a disc of some radius $r$. Eq.~\ref{eq:single-cost-simple} derives the cost estimate for a single arm solution as approximately $(c_{pd} + 0.52c_t)n$. Firstly the following arguments can be made for $k$-arms.

\tase{

\begin{theorem}
	\textit{A $k$-arm solution can have an 
	asymptotic improvement of $\frac{1}{k}$ over the single arm solution, when rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square.}
\end{theorem}

\textit{Proof:}	
%\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
\commentadd{%The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
	for each arm to work with. Consider the transfers and transits of a set of $k$ 
	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
	can be achieved in a bounded region with a perimeter of $O(kr)$. 
	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential cost that can be incurred,  a $k$-arm solution has a cumulative cost of:

	The cost ratio is
% 	\vspace{-0.1in}
	\begin{align*}\label{eq:kmakespan-ratio}
	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
	% \vspace{-0.1in}
	\end{align*}

    }
}

For obtaining a $2$-arm solution, first partition the $n$ objects randomly into two sets of $\frac{n}{2}$ objects each. Then, obtain the two initial solutions similar to the single arm case.  
% It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves should add up to approximately $(c_{pd} + 0.52c_t)n$. 
% The reasoning follows Lemma \ref{lem:transferdomination}, which states that transfers dominate the cost of the solution.

\begin{corollary}
	\textit{A $2$-arm solution can have an asymptotic improvement of $\frac{1}{2}$ over the single arm solution for rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square}
	\label{thm:karm}
\end{corollary}

\textit{Proof: }
From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
solution that is collision-free. Assume that pickups and drop-offs can be achieved without collisions between the two arms, which can be achieved with properly designed end-effectors. The main overhead is then the potential collision between the two (disc) arms during transfer and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
with, an arm may travel a path formed by $n + 1$ straight line 
segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
two end-effector trajectories where potential collisions may happen. Nevertheless, since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle. For each intersection, let one 
arm wait while the other circles around the first arm, which incurs a cost that is bounded by $2\pi \cdot r \cdot c_t$.

Adding up all the potential cost that a $2$-arm solution can incur, the following cumulative cost is obtained:

@@

\noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$, and
$c_t$ is a distance (e.g., energy) cost. Upon considering the maximum of the two arc lengths or makespan (Eq.~\ref{eq:cost_function}),
the $2$-arm cost becomes $C_{\rm dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$.

The cost ratio is
%\vspace{-0.1in}
\begin{align*}%\label{eq:makespan-ratio}
\frac{C_{\rm dual}^t}{C_{\rm single}} &\approx 
\frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
\\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;\numberthis \label{eq:dualasync}
% \vspace{-0.1in}
\end{align*}

@@

\begin{theorem}
	\textit{For rearranging objects with non-overlapping starts and goals that are 
	uniformly distributed in a unit square,  a randomized $2$-arm \textit{synchronized} solution can have an 
	asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and an improvement of roughly $0.64$ when both $c_{pd}$ and $r$ are small. }
\label{thm:syncproof}
\end{theorem}

\textit{Proof:} 
\tase{
In preparation for the proof of Theorem \ref{thm:syncproof}, we develop the following lemma.
\begin{lemma}
	The expected measure of the maximum of lengths of two random lines on a unit square is $ 0.66 $.
\end{lemma}

\textit{Proof:} Prior work \cite{ghosh1951random} defines the \textit{probability distribution function (pdf)} of lengths($\ell$) of randomly sampled lines in a rectangle.
% of sides $a,b, \ \ a\geq b$.
% as 
%\begin{align*}
%p(l) &= (\frac{4l}{a^2b^2})\phi(l)\\
%\phi(l)&= \frac{1}{2}\pi a b - a l - b l + \frac{1}{2} l^2, \ \ l\in[0,b]\\
%\phi(l)&= ab \sininv(\frac{b}{l}) + a. \sqrt[]{(l^2-b^2)} - al - \frac{1}{2}b^2, \ \ l\in[b,a]\\
%\phi(l)&= ab\{\sininv(\frac{b}{l})-\cosinv(\frac{a}{l})\} + a\sqrt[]{(l^2-b^2)} + b\sqrt[]{(l^2-a^2)} \\
%&- \frac{1}{2}(l^2+a^2+b^2),\ \ l\in[a,\sqrt[]{(a^2+b^2)}]
%\end{align*}

%In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
Substituting the values for the dimensions of the rectangle in the unit square model, the \textit{pdf} can be simplified as follows.
\begin{align*}
p(\ell)&= 2\pi \ell - 8\pi \ell^2 + 2\ell^3, \ \ \ell\in[0,1]\\
p(\ell)&= 4\ell\sininv\!\!\left(\frac{1}{\ell}\right)\!- 4\ell\cosinv\!\!\left(\frac{1}{\ell}\right)\!+ 8\ell\sqrt{\ell^2-1} -2\ell^3 -4\ell,\\ &\ \ell\in[1,\sqrt[]{2}],
\end{align*}
where $\ell$ is the length measure, and $p(\ell)$ is the probability measure over different lengths.
Assuming two random sets of lines, representing transfers in a random split of objects between two arms, the expected value of the maximum of these pairwise lengths i.e., $\mathtt{E}(\max(\ell_1,\ell_2)), \ \ \ell_1,\ell_2\ i.i.d, \ \ \ell_1 \sim p, \ell_2 \sim p$, can be estimated using the \textit{pdf} obtained. 
\begin{align*}
\mathtt{E}(\max(\ell_1,\ell_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} \max(\ell_1,\ell_2)p(\ell_1)p(\ell_2) d\ell_2 d\ell_1\\&\approx 0.663
\end{align*}
% \vspace{-0.1in}
% The result is calculated by taking into account the combination of different ranges of $p(\ell)$ and $\max(\ell_1,\ell_2)$.
\commentadd{
%	\begin{figure}[h]
%		\centering
%		%	\vspace{-0.3in}
%		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
%		\caption{Empirical cost ratio versus the estimate}
%		\label{fig:mcbounds}
%	\end{figure}
	Prior work~\cite{santalo2004integral} offered an estimate for the expected length of a transit path $C_{sg}$ in terms of the expected length of a line segment, $0.52$, in a randomized setting in a unit square. With the current estimate of $0.66$ for the maximum of two such randomly sampled line segments, it follows that, the expected makespan or maximum of distances cost will use this estimate.

	\qed

@@

Now all the tools necessary for the proof of Theorem \ref{thm:syncproof} are available.

The synchronization assumption changes the expected cost of the solution. The random partitioning of the $n$ objects into two sets of $\frac{n}{2}$ object with a random ordering of the objects yields $\frac{n}{2}$ pairs of objects transfers, which dominate the total cost for large $n$. The cost~(Eq.~\ref{eq:cost_function}) of $\frac{n}{2}$ synchronized transfers ($\coma_i$) includes $\frac{n}{2}c_{pd}$ and $C^{\rm sync}_{sg} \approx (\mathtt{E}(\max(\ell_1,\ell_2))c_t)\frac{n}{2}$, where $\mathtt{E}(\max(\ell_1,\ell_2))$ is the expected measure of the maximum of lengths $\ell_1$,$\ell_2$ of two randomly paired transfers. 
% This value is deduced in the next section.

%Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$ .

% (Section \ref{sec:appendix}).

It follows that $C_{\rm dual}^{\rm sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$.
% \vspace{-0.1in}
% \begin{equation}\label{eq:synchronized-cost}
% C_{dual}^{sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t
% \vspace{-0.1in}
% \end{equation}
% {\centerline
% {
% $C_{dual}^{sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$
% }
% }
The synchronized cost ratio is
%\vspace{-0.1in}
\begin{align*}\label{eq:synchronized-ratio}
\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} &\approx 
\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
\\&= \frac{1}{2} + \frac{ (0.07 + 4\pi r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
%\vspace{-0.1in}
\end{align*}

When $\frac{c_t}{c_{pd}}$ is small, even the synchronized $2$-arm solution provides an improvement of $\frac{1}{2}$. For the case when both $r$ and $c_{pd}$ are small, we observe that the ratio approaches $0.636$.\qed 
\commentdel{Fig \ref{fig:bounds} confirms empirically that in randomized trials on an unit square, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, converges to the calculated estimate (red line).}

\tase{
	\begin{figure}[h]
		\centering
% 		\vspace{-0.1in}
		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
		\caption{ \tase{ Empirical cost ratio $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0, r=0$ in the unit square model, versus the estimate (red line). As the number of object transfers increases the measured value converges to the estimate. } }
		\label{fig:mcbounds}
		\vspace{-0.1in}
	\end{figure}
	As a way to validate our asymptotic estimate, randomized trials were run with different number of randomly sampled object transfer coordinates on an unit square.
% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$. Fig \ref{fig:mcbounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
}

%\vspace{-0.08in}
%\begin{theorem}
%For rearranging objects with non-overlapping starts and goals that are 
%uniformly distributed in a unit square,  a randomized $2$-arm synchronized solution can have an 
%asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. 
%\end{theorem}

\commentadd{
\noindent \textbf{Note on bounds:} Even though the proposed simplified model may not be
immediately suitable for general configuration spaces, experiments indicate that the speedups exist in these spaces as well.
}
% \rahul{this paragraph is phrased contradictorily. It makes sense if the first sentence is for asynchronous cases.}
% We note that the same can be said for a {\em synchronous} $2$-arm solution if
% when $c_t/c_{pd}$ is small. 
% Under the synchronization assumption, $C_{dual}^t$
% is no longer necessarily expected to be $\frac{C_{single}}{2}$ for large $n$. 
% Experiments in the next section indicate that improvements over single arm solutions in practical settings.
